---
title: "Expt 4 - TwoNames"
output: html_document
author: "Hugh Rabagliati"
---

This is the basic behavioral analysis for Experiment 4, looking at children's naming. There are two types of trials, control and ambiguous. The target is always second; on critical trials it is proceeded by something with the same name. We have 16 participants right now; we'd like more. 


```{r}
library(doBy)
library(lme4)
TwoNames <- read.csv("TwoNames.csv", header = T)
summaryBy(Label+Age~Condition+Order, data = TwoNames)
```

This analysis compares labels from the first and second pictures of the ambiguous trials.

```{r}
summary(glmer(Label~Order + (1|Participant.Name) + (1|Target.Name), data = TwoNames[TwoNames$Condition != "Control",], family = "binomial"))

```

The next analysis is based on the hypothesis that Unambig (second name) should have less modification than Ambiguous (first name), which should have less modification than Ambiguous (second name).

We have to write a function to do forward difference regression coding first:

```{r}
forward_diff <- function(k){ # k = number of levels of the factor
j <- k-1
fd <- matrix(NA, nrow =k, ncol = j , dimnames = list(1:k,1:j))

r = 1
for (h in 1:j){
  for (i in 1:k){
		if (i <= r){
			fd[i,h] <- (k-r)/k
				}else{
			fd[i,h] <- -r/k
			}
		}
	r <- r+1
}
return(fd)
}
```

Then create the relevant factor, change it's contrasts, and run the analysis.

```{r}

TwoNames$Ordering <- 1
TwoNames[TwoNames$Condition == "Control" & TwoNames$Order == 1,]$Ordering <- NA
TwoNames[TwoNames$Condition == "Ambig" & TwoNames$Order == 1,]$Ordering <- 2
TwoNames[TwoNames$Condition == "Ambig" & TwoNames$Order == 2,]$Ordering <- 3

TwoNames$Ordering <- as.factor(TwoNames$Ordering)
contrasts(TwoNames$Ordering) <- forward_diff(length(levels(TwoNames$Ordering)))

summary(glmer(Label~as.factor(Ordering) + (1|Participant.Name) + (1|Target.Name), data = TwoNames, family = "binomial"))
```
