---
title: "Analysis of Children's Data in Expt 2"
author: "Hugh Rabagliati"
date: "2 November 2014"
output: html_document
---

```{r}
require(lme4)
require(doBy)
require(plyr)
load("kidsac.RDATA")

```


First, some data processing. Each child's utterance is coded for whether it is potentially ambiguous.
```{r}
 #Create LabelCond variable; used for data analysis
kid.sac$LabelCond <- NA
kid.sac[kid.sac$cond == "Control" & kid.sac$Label %in% c(1,0),]$LabelCond <- "Control"
kid.sac[kid.sac$cond == "Ambig" & kid.sac$Label %in% c(1),]$LabelCond <- "Test-Ambig"
kid.sac[kid.sac$cond == "Ambig" & kid.sac$Label %in% c(0),]$LabelCond <- "Test-Unambig"
kid.sac$LabelCond <- as.factor(kid.sac$LabelCond)
# Exclude kids with no utterance data
kid.sac <- kid.sac[!is.na(kid.sac$LabelCond),]
kid.sac <- kid.sac[!kid.sac$AgeGroup == "Excl",]
kid.sac <- kid.sac[!kid.sac$Lang == "Exc",]
```

and we define time periods before/after onset of the utterance.

```{r}
# Discern when the name was said.
 kid.sac$Start <- "Before"
 kid.sac[kid.sac$Period == "Naming",]$Start <- ifelse(kid.sac[kid.sac$Period == "Naming",]$SacTime < kid.sac[kid.sac$Period == "Naming",]$StartTime,"Before","After")
 #kid.sac[kid.sac$Period == "Pre",]$Start <- ifelse(kid.sac[kid.sac$Period == "Pre",]$SacTime < 2250 ,"Before","After")
  kid.sac[kid.sac$Period == "Rew",]$Start <- "After"
```


Finally, we create our data frame for analysis
```{r}
   summaryBy(SacDist1+SacDist2+SacFromTarg+SacToTarg +SacTarg ~AgeGroup+Subj+trialnum+LabelCond+Period+Start, data = kid.sac, keep.names = T) -> Sac.sum
   na.omit(summaryBy(SacTarg +SacDist2 +SacDist1+SacFromTarg+SacToTarg ~AgeGroup+Period+Start+LabelCond, data = Sac.sum, keep.names = T))

```

**Demographics & Responses**

We have `r length(unique(Sac.sum[!is.na(Sac.sum$LabelCond),]$Subj))` subjects.

```{r}
subj <- summaryBy(Label~Subj + trialnum + Lang + AgeGroup+ cond, data = kid.sac,keep.names = T, na.rm = T)
subj <- summaryBy(Label~Subj + Lang + AgeGroup+ cond, data = kid.sac,keep.names = T, na.rm = T)
summaryBy(Label~Lang + AgeGroup+ cond, data = subj, FUN = c(mean, length))
```


**Eye tracking analysis**

Now, we plot saccades between the Target picture and its Foil for each time window, based on children's utterance.

```{r, echo=FALSE}
na.omit(summaryBy(SacTarg~Period+Start+LabelCond+Subj, data = Sac.sum[Sac.sum$Period != "Rew",], FUN = c(mean,sd), keep.names = T)) -> Sac.graph
na.omit(summaryBy(SacTarg.mean~Period+Start+LabelCond, data = Sac.graph, FUN = c(mean,sd))) -> Sac.graph
Sac.graph$Period <- factor(Sac.graph$Period, levels = c("Pre","Naming"),labels = c("Pre","Naming"), ordered = T)
Sac.graph$Start <- factor(Sac.graph$Start, levels = c("Before","After"),labels = c("Before","After"), ordered = T)
Sac.graph$SE = Sac.graph$SacTarg.mean.sd/sqrt(length(unique(Sac.sum$Subj)))

Sac.graph$Time = "Pre-Naming"
Sac.graph[Sac.graph$Start == "After" , ]$Time = "Post-Naming"
Sac.graph[Sac.graph$Period == "Pre" , ]$Time = "Preview"
Sac.graph$Time <- factor(Sac.graph$Time, levels = c("Preview","Pre-Naming","Post-Naming"),labels = c("Preview","Pre-Naming","Post-Naming"), ordered = T)

tapply(Sac.graph$SacTarg.mean.mean, list(Sac.graph$Time,Sac.graph$LabelCond), FUN = mean) -> o
tapply(Sac.graph$SE, list(Sac.graph$Time,Sac.graph$LabelCond), FUN = mean) -> se

barplot(o, beside =T , ylim = c(0,0.25),col = "white",  border = NA, ylab = "Proportion actions using Instrument", names.arg = c("Preview", "Pre-Naming","Post-Naming"))
legend(1.2,0.10, legend = c("Control", "Ambiguous Description", "Unambiguous Description"), bty = "n", col = c("blue","grey","red"), pch = 20)
points(c(1.5,6,10), o[,1], pch = 20, cex = 2, col = "blue")
points(c(2.5,6.8,11), o[,2], pch = 20, cex = 2, col = "grey")
points(c(3.5,7.6,12), o[,3], pch = 20, cex = 2, col = "red")
grid(nx = NA, ny = NULL, col = "gray", lty = "dotted",lwd = par("lwd"), equilogs = TRUE)
abline(v = c(4.5,8.5), col = "grey", lty = "dashed")
arrows(c(1.5,6,10,2.5,6.8,11,3.5,7.6,12), (c(o) + c(se)+0.01), c(1.5,6,10,2.5,6.8,11,3.5,7.6,12), (c(o) - c(se)-0.01), code = 0)
```


We use mixed effects models to analyze each time window.
```{r}
summary(lmer(SacTarg~LabelCond+ (1+LabelCond|Subj), data = subset(Sac.sum, AgeGroup !="Excl" & Period == "Pre")))
summary(lmer(SacTarg~LabelCond+ (1+LabelCond|Subj), data = subset(Sac.sum, AgeGroup !="Excl" & Period == "Naming" & Start == "Before")))
summary(lmer(SacTarg~LabelCond+ (1+LabelCond|Subj), data = subset(Sac.sum, AgeGroup !="Excl" & Period == "Naming" & Start == "After")))   	 

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
